%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[10pt,letterpaper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{classic}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.82]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...
\usepackage{fancyhdr}
\pagestyle{fancy}
% \lhead{Curriculum Vitae\\Stanford University - Department of Aeronautics and Astronautics}
\lhead{Curriculum Vitae\\Department of Aerospace Engineering\\U-M ID: 29804372}
% personal data
\name{Hongyi}{Xia}
%\title{Resumé title}                               % optional, remove / comment the line if not wanted
\address{11048 Amherst Ave.}{Silver Spring, MD 20902}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+1~(301)~541~7635}                   % optional, remove / comment the line if not wanted
\email{hongyi.xia@gmail.com}                               % optional, remove / comment the line if not wanted
\homepage{www.linkedin.com/in/hongyixia}                         % optional, remove / comment the line if not wanted
%\extrainfo{additional information}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
\usepackage{multibib}
\usepackage{textgreek}
\usepackage[T1]{fontenc}
\usepackage{tgpagella}
\usepackage{dtklogos}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

\section{Education}
\cventry{2010--2015 Expected}{B.S. Aerospace Engineering}{University of Maryland College Park}{College Park}{MD}{Aerospace Engineering Honors Program}  % arguments 3 to 6 can be left empty
\cventry{2006--2010}{High School}{Montgomery Blair High School}{Silver Spring}{MD}{Science, Mathematics, and Computer Science Magnet Program}

%\section{Master thesis}
%\cvitem{title}{\emph{Title}}
%\cvitem{supervisors}{Supervisors}
%\cvitem{description}{Short thesis abstract}

\section{Experience}
\subsection{Industry}
\cventry{September 2013--August 2014}{Propulsion Intern}{Space Exploration Technologies}{Hawthorne, CA}{}{
\begin{itemize}
\item Developed software to visualize 3D combustion simulations of the Raptor rocket engine in C++ and OpenGL. Integrated with Leap Motion sensor for interaction via hand gestures.
\item CFD and thermal analysis of the Merlin 1D rocket engine, Crew Dragon vehicle, Falcon 9 v1.1 vehicle, and Falcon 9 v1.1 developmental vehicle in ANSYS CFX, Star-CCM+, and Thermal Desktop to aid design, ensure correct operation of various components, and to keep on schedule for flight vehicle development and production.
\item Created algorithms to automate data review of the Merlin 1D and Merlin Vacuum engine. Complete rewrite of current engine performance code to calculate engine parameters of single engine acceptance test data and stage test data for improved readability, accuracy, and consistency. Built an understanding of the engine fluid system, core rocket equations, pump maps, stage calculations etc.
\item Supported daily operations of the Liquid Engine Development team in data review and flight data acquisition during launch operations. Developed application to support flight data acquisition.
\end{itemize}}
\cventry{September--December 2012}{Entrepreneurial Consultant}{Science Applications International Corporation}{College Park, MD}{}{Researched and wrote recommendation report on waste heat recovery systems for military engines as part of an entrepreneurial consulting engagement partnered through Hinman CEOs.}
\subsection{Research}
\cventry{June--August 2013}{Research Intern}{Interaction Lab, University of Southern California}{Los Angeles, CA}{}{Developed exercises for the NAO robot, an exercise buddy for overweight children in an obesity intervention study. Participated in the Viterbi Summer Undergraduate Research Experience (SURE) program.}
\cventry{June 2010-- May 2013}{Research Intern}{Collective Dynamics and Control Laboratory University of Maryland}{College Park, MD}{}{
\begin{itemize}
\item Designed and performed flow visualization experiments to validate a potential flow model. Research culminated in paper titled ``Experimental Flow Visualization of Karman Vortex Flow past a Fish-inspired Robot''. Presented at the 2013 AIAA Region I-MA Student Conference. (2012-2013)
\item Wrote Matlab simulations to model the dynamics of rigid body collisions to study collective behavior of hexbugs. (2011)
\item Developed a motion coordination algorithm for Lego NXT that enables two robotic tanks to balance on a seesaw. (2010)
\end{itemize}}

\cventry{June--August 2012}{Research Intern}{Miniature Robotics REU Program, University of Maryland}{College Park, MD}{}{Developed a method to visualize 3D flows using Microsoft Kinect as a sensor. Calibrated and programmed Microsoft Kinect cameras in OpenCV and Python to collect depth video data. Wrote Matlab scripts to image process depth video data of smoke rings and calculate their flow properties.}
\cventry{June--August 2009}{Research Intern}{National Institutes of Health}{Bethesda, MD}{}{Research culminated in paper titled ``Determination of the Effect of Modifying G\textbeta5 Expression Levels on Drosophila Oxidative Stress Resistance.'' Placed semi-finals in Siemens Competition in Math, Science, and Technology.}


\section{Teaching and Mentoring}
\cventry{September 2012--May 2013}{Math Coach, Math Success Program}{University of Maryland}{College Park, MD}{}{Tutored students in undergraduate math courses.}
\cventry{September 2011--May 2013}{Peer Mentor, SEEDS Peer Mentoring Program,}{University of Maryland, }{College Park, MD}{}{Mentored a group of 10 freshman engineering students to facilitate their adjustment to college and the engineering program each year.}
\cventry{January--May 2012}{Teaching Fellow, ENES232 Thermodynamics}{University of Maryland}{College Park, MD}{}{Facilitated recitation for 60 students. Graded student quizzes. Held weekly office hours.}


\section{Languages}
\cvitemwithcomment{Mandarin}{Fluent}{Native Speaker}
\cvitemwithcomment{English}{Fluent}{Lived in the United States since age 6}

\section{Computer skills}
\cvitem{Languages}{Matlab, Java, Python, C++, OpenGL, git, \LaTeX}
\cvitem{Applications}{ANSYS, Star-CCM+, Thermal Desktop, Autodesk Inventor, Siemens NX, Visual Studio}
\cvitem{Operating Systems}{Linux, Mac OS X, Windows}

\section{Academic Honors}
\cvlistitem{1st Place, JP Morgan Code for Good Challenge - Delaware 2014}
\cvlistitem{Banneker Key Scholar - Full, four year scholarship to the University of Maryland (2010-2014)}
\cvlistitem{Siemens Competition in Math, Science, and Technology Semifinalist 2009}
\cvlistitem{Maryland Distinguished Scholar Finalist (Academic Achievement) 2009}
\cvlistitem{National AP Scholar 2009}

\section{Affiliations}
\cvlistitem{Hinman CEOs - A living and learning entrepreneurship program at the University of Maryland}
\cvlistitem{AIAA - American Institute of Aeronautics and Astronautics}
\cvlistitem{Tau Beta Pi - National Engineering Honor Society, inducted December 2011.}
\cvlistitem{Sigma Gamma Tau - National Aerospace Engineering Honor Society, inducted December 2011.}
\cvlistitem{Alpha Omega Epsilon - Professional Engineering Sorority}




%\section{Extra 2}
%\cvlistdoubleitem{Item 1}{Item 4}
%\cvlistdoubleitem{Item 2}{Item 5\cite{book1}}
%\cvlistdoubleitem{Item 3}{Item 6. Like item 3 in the single column list before, this item is particularly long to wrap over several lines.}

%\section{References}
%\begin{cvcolumns}
%  \cvcolumn{Category 1}{\begin{itemize}\item Person 1\item Person 2\item Person 3\end{itemize}}
%  \cvcolumn{Category 2}{Amongst others:\begin{itemize}\item Person 1, and\item Person 2\end{itemize}(more upon request)}
%  \cvcolumn[0.5]{All the rest \& some more}{\textit{That} person, and \textbf{those} also (all available upon request).}
%\end{cvcolumns}

% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"):
\renewcommand{\refname}{Presentations}
% \nocite{*}
\section{Publications and Presentations}
% \bibliographystyle{plain}
% \bibliography{publications}                        % 'publications' is the name of a BibTeX file
\begin{thebibliography}{1}
\bibitem{aiaa} Hongyi Xia. {\em Experimental Flow Visualization of Karman Vortex Flow past a Fish-inspired Robot.}  2013: AIAA Region I-MA Student Conference.
\bibitem{nao} Hongyi Xia. {\em Designing Exercises for the NAO as an Exercise Buddy in an Obesity Intervention Study.} 2013: University of Southern California Viterbi School of Engineering Summer Undergraduate Research Experience Final Presentation.
\bibitem{minirobot}  Hongyi Xia. {\em 3D Flow Visualization using Microsoft Kinect} 2012:
Miniature Robotics Research Experiences for Undergraduates Program Final Presentation University of Maryland College Park.
\bibitem{siemens} Hongyi Xia. {\em Determination of the Effect of Modifying G$\beta$5 Expression Levels on Drosophila Oxidative Stress Resistance} 2009: Placed as semifinalist in the Siemens Competition in Math, Science, and Technology.
\end{thebibliography}
% Publications from a BibTeX file using the multibib package
% \section{Publications}
%\nocitebook{book1,book2}
% \bibliographystylebook{plain}
% \bibliographybook{publications}                   % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliography{publications}                   % 'publications' is the name of a BibTeX file



%\clearpage\end{CJK*}                              % if you are typesetting your resume in Chinese using CJK; the \clearpage is required for fancyhdr to work correctly with CJK, though it kills the page numbering by making \lastpage undefined
\end{document}


%% end of file `template.tex'.
